oREV item selection

### 2022-11-07 analysis/item_selection.Rmd

@@

## Rasch model fir for selected items

```{r}
irt1_sel <- readRDS("../saves/irt1_sel.rds")

rasch_fit_sel <- irt_dat%>%
  select(-order, -sex)%>%
  filter(targetWord %in% rasch_sel_items,
         #subjID %in% c("15X7mwV1", "39tVizn3", "479FefBH")
         )%>%
  add_epred_draws(irt1_sel, re_formula = ~(1 | targetWord) + (1 | subjID), ndraws = 5000)%>%
  mutate(zvi = (correct - .epred)/(.epred*(1-.epred))^0.5)%>%
  group_by(targetWord,aoa_german_comb, .draw)%>%
  summarise(outfit = sum(zvi^2)/length(unique(subjID)),
            infit = (sum(zvi^2*(.epred*(1-.epred)))/sum(.epred*(1-.epred))))
```

```{r}
rasch_fit_sel%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index))+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,10)+
  theme_bw()
```

>>>>

   sim <- simulated_annealing(25)

@@
